\section{Setting up Encrypted Instant Messaging}

\subsection{Android - Installing Gibberbot}

\href{https://guardianproject.info/apps/gibber/}{https://guardianproject.info/apps/gibber/}

Gibberbot is a secure chat client capable of end-to-end encryption. It
works with Google, Facebook, any Jabber or XMPP server. Gibberbot uses
the Off-The-Record encryption standard (OTR) to enable true verifiable
end-to-end encrypted communications.

You can install Gibberbot through the Google Play store or from another
trusted source.

You can securely chat with other programs with OTR support such as
Adium, Pidgin on the desktop, Gibberbot on Android or ChatSecure on iOS.

\subsection{iOS - Installing ChatSecure}

\href{http://chrisballinger.info/apps/chatsecure/}{http://chrisballinger.info/apps/chatsecure/}

ChatSecure is a secure chat client capable of end-to-end encryption. It
works with Google, Facebook, any Jabber or XMPP server. ChatSecure uses
the Off-the-Record encryption standard (OTR) to enable true verifiable
end-to-end encrypted communications.

You can install ChatSecure through the iTunes store

You can securely chat with other programs with OTR support such as
Adium, Pidgin on the desktop, Gibberbot on Android or ChatSecure on iOS.

\subsection{Ubuntu - Installing Pidgin}

\href{http://pidgin.im/}{http://pidgin.im/}

Pidgin is a secure chat client capable of end-to-end encryption. It
works with Google, Facebook, any Jabber or XMPP server. Pidgin uses the
Off-the-Record encryption standard (OTR) to enable true verifiable
end-to-end encrypted communications.

You can install via Ubuntu Software Center, search for pidgin-otr to
install pidgin and the pidgin otr plugin.

Once installed you can enable otr for any account you setup in pidgin.

You can securely chat with other programs with OTR support such as
Adium, Pidgin on the desktop, Gibberbot on Android or ChatSecure on iOS.

\subsection{OS X - Installing Adium}

\href{http://www.adium.im/}{http://www.adium.im/}

Adium is a secure chat client capable of end-to-end encryption. It works
with Google, Facebook, any Jabber or XMPP server. Adium uses the
Off-the-Record encryption standard (OTR) to enable true verifiable
end-to-end encrypted communications.

Installing Adium is similar to installing most Mac OS X applications.

\begin{enumerate}[1.]
\item
  Download the Adium disk image from http://www.adium.im/.
\item
  If an Adium window doesn't open automatically, double click the
  downloaded file
\item
  Drag the Adium application to your Applications folder.
\item
  ``Eject'' the Adium disk image, which has an icon of a drive
\item
  The Adium disk image will still be present in your download folder
  (probably on your desktop). You can drag this file to the trash, as it
  is no longer needed.
\item
  To load Adium, locate it in the Applications folder and double click.
\end{enumerate}
You can securely chat with other programs with OTR support such as
Adium, Pidgin on the desktop, Gibberbot on Android or ChatSecure on iOS.

\subsection{Windows - Installing Pidgin}

\href{http://pidgin.im/}{http://pidgin.im/}

Pidgin is a secure chat client capable of end-to-end encryption. It
works with Google, Facebook, any Jabber or XMPP server. Pidgin uses the
Off-the-Record encryption standard (OTR) to enable true verifiable
end-to-end encrypted communications.

To use Pidgin with OTR on Windows, you have to install Pidgin and the
OTR plugin for Pidgin.

\begin{enumerate}[1.]
\item
  Download the latest version of Pidgin from
  http://www.pidgin.im/download/windows/
\item
  Run the Pidgin Installer
\item
  Download the latest version of ``OTR plugin for Pidgin'' from
  http://www.cypherpunks.ca/otr/\#downloads
\item
  Run the OTR Plugin Installer
\end{enumerate}
Now you can use OTR with any account you setup in Pidgin.

You can securely chat with other programs with OTR support such as
Adium, Pidgin on the desktop, Gibberbot on Android or ChatSecure on iOS.

\subsection{All OS - crypto.cat}

\href{https://crypto.cat}{https://crypto.cat}

Cryptocat is an open source web application intended to allow secure,
encrypted online chatting. Cryptocat encrypts chats on the client side,
only trusting the server with data that is already encrypted. Cryptocat
is delivered as a browser extension and offers plugins for Google
Chrome, Mozilla Firefox and Apple Safari.

Cryptocat intends to provide means for impromptu, encrypted
communications that offer more privacy than services such as Google
Talk, while maintaining a higher level of accessibility than other
high-level encryption platforms, and furthermore allows for multiple
users in one chat room.

\subsection{Chat Log Files}

Some of the Chat Clients listed above e.g.~Adium, store plaintext,
unencrypted Chat Logs, often by default, even when the OTR ``security /
privacy'' plug-in is installed.

If you are taking OTR precautions to protect your chats from snoopers
over the wire or over the air, you should either double check that you
have manually switched off Chat Session Logging, or ensure that the Chat
Logs you deliberately intend to keep are created on an encrypted disk
drive or volume, in case your computer is lost, stolen or seized. It is
also worth asking the person you are chatting with if they are
inadvertently logging the chat with their own Chat Client software.
