\section{Extending Google Chrome}

Chrome is Google's browser. Here are some useful tips and extensions:

\subsection{Disabling Instant Search}

Chrome can search as you type. The advantage of this is that you get
search suggestions and can use Google's predictions - but the
disadvantage is that every character you type is sent to Google's
servers, where it may be logged.

To disable, open Chrome's settings by clicking the menu button at the
right of the address bar and clicking Settings. Or, simply type
\verb!chrome://settings/! in your address bar.

Ensure that the \textbf{Enable Instant for faster searching (omnibox
input may be logged)} checkbox is unchecked.

\subsection{AdBlock for Chrome}

Just like Firefox, AdBlock removes ads. Install from
\href{https://chrome.google.com/webstore/detail/adblock/gighmmpiobklfepjocnamgkkbiglidom}{this
Chrome Webstore page}.

\subsection{HTTPS Everywhere}

Forces encrypted https connections wherever possible. Installation link
can be found on the \href{https://www.eff.org/https-everywhere}{EFF
HTTPS Everywhere homepage}.

\subsection{PrivacyFix}

PrivacyFix (beta) gives you a dashboard view of your privacy settings on
Facebook and Google, as well as Do-Not-Track headers and tracking
cookies. It provides links to quickly change these privacy settings
without digging through many drilldown pages. Install from the
\href{https://chrome.google.com/webstore/detail/privacyfix-by-privacychoi/pmejhjjecaldkllonlokhkglbdbkdcni}{Chrome
web store page}
