\section{About This Book}

The CryptoParty Handbook was born from a suggestion by Marta Peirano
(\href{http://petitemedia.es}{http://petitemedia.es}) and Adam Hyde
(\href{http://booksprints.net}{http://booksprints.net}) after the first
Berlin CryptoParty, held on the 29th of August, 2012. Julian Oliver
(\href{http://julianoliver.com}{http://julianoliver.com}) and Danja
Vasiliev (\href{http://k0a1a.net}{http://k0a1a.net}), co-organisers of
the Berlin CryptoParty along with Marta were very enthusiastic about the
idea, seeing a need for a practical working book with a low
entry-barrier to use in subsequent parties. Asher Wolf, originator of
the Crypto Party movement, was then invited to run along and the project
was born.

This book was written in the first 3 days of October 2012 at Studio
Weise7, Berlin, surrounded by fine food and a small ocean of coffee.
Approximately 20 people were involved in its creation, some more than
others, some local and some far.

The writing methodology used, BookSprint
(\href{http://booksprints.net}{http://booksprints.net}), is all about
minimising any obstruction between expertise and the published page.
Face-to-face discussion and dynamic task-assignment were a huge part of
getting the job done, like any good CryptoParty!

The open source, web-based (HTML5 and CSS) writing platform BookType
(\href{http://booktype.pro}{http://booktype.pro}) was chosen for the
editing task, helping such a tentacular feat of parallel development to
happen with relative ease. Asher also opened a couple of TitanPad pages
to crowd-source the Manifesto and HowTo CryptoParty chapters.

Combined, this became the official CryptoParty Handbook by midnight
October the 3rd, GMT+1.

The Book Sprint was 3 days in length and the full list of onsite
participants included:

Adam Hyde (facilitator), Marta Peirano, Julian Oliver, Danja Vasiliev,
Asher Wolf (\href{http://cryptoparty.org}{http://cryptoparty.org}), Jan
Gerber, Malte Dik, Brian Newbold, Brendan Howell
(\href{http://wintermute.org}{http://wintermute.org}, AT, Carola Hesse,
Chris Pinchen
(\href{http://chokepointproject.net}{http://chokepointproject.net/}).
Cover art (illustrations to come) by Emile Denichaud
(\href{http://about.me/denichaud}{http://about.me/denichaud})

This version of the handbook has since moved to github to
collaboratively edit it. Find it at
\href{https://github.com/cryptoparty/handbook}{https://github.com/cryptoparty/handbook}.
If you see areas that need improvement or simply come across a typo,
create a github account and start editing, commenting or creating
issues. For help using git and github, see
\href{https://help.github.com/}{https://help.github.com/}.

CryptoParty HandBook Credits

Facilitated by:

\begin{itemize}
\item
  Adam Hyde
\end{itemize}
Core Team:

\begin{itemize}
\item
  Marta Peirano
\item
  Asher Wolf
\item
  Julian Oliver
\item
  Danja Vasiliev
\item
  Malte Dik
\item
  Jan Gerber
\item
  Brian Newbold
\item
  Brendan Howell
\end{itemize}
Assisted by:

\begin{itemize}
\item
  Teresa Dillon
\item
  AT
\item
  Carola Hesse
\item
  Chris Pinchen
\item
  `LiamO'
\item
  `l3lackEyedAngels'
\item
  `Story89'
\item
  Travis Tueffel
\end{itemize}
Cover Image by Emile Denichaud.

Other material included:

\begin{itemize}
\item
  \href{https://www.flossmanuals.net/bypassing-censorship}{https://www.flossmanuals.net/bypassing-censorship}
\end{itemize}
The manuals used in the second half of this book borrow from 2 books
sprinted by FLOSS Manuals:

\begin{itemize}
\item
  ``How to Bypass Internet Censorship'' 2008 \& 2010 Adam Hyde
  (Facilitator), Alice Miller, Edward Cherlin, Freerk Ohling, Janet
  Swisher, Niels Elgaard Larsen, Sam Tennyson, Seth Schoen, Tomas Krag,
  Tom Boyle, Nart Villeneuve, Ronald Deibert, Zorrino Zorrinno, Austin
  Martin, Ben Weissmann, Ariel Viera, Niels Elgaard Larsen, Steven
  Murdoch, Ross Anderson, helen varley jamieson, Roberto Rastapopoulos,
  Karen Reilly, Erinn Clark, Samuel L. Tennyson, A Ravi
\item
  ``Basic Internet Security'' 2011 Adam Hyde (Facilitator), Jan Gerber,
  Dan Hassan, Erik Stein, Sacha van Geffen, Mart van Santen, Lonneke van
  der Velden, Emile den Tex and Douwe Schmidt
\end{itemize}
The CryptoPart Handbook content is licensed under the
\href{https://creativecommons.org/licenses/by-sa/3.0/}{Creative Commons
Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0)}.

All chapters © the contributors unless otherwise noted below.
